---
title: "DS4002_project1"
author: "Campbell Hogg"
date: "1/4/2022"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r}

## PROJECT DESCRIPTION

**Objective:**


**Data Set:**

```{r}
library(tidyverse)
library(plotly)
library(htmltools)
library(devtools)
#library(caret)
library(NbClust)
library(dplyr)
```


```{r}
#read in the data
Data = read.csv("~/Desktop/College_Data_Project1.csv")

###EDA
#find correlations for variable selection
salary = as.numeric(Data[,"Median.Salary"])
sfratio = as.numeric(Data[,"S.F.Ratio"])
gradrate = as.numeric(Data[,"Grad.Rate"])
top10 = as.numeric(Data[,"Top10perc"])

#WAYS TO CHECK CORRELATION BETWEEN VARIABLES AND SALARY
cor(gradrate, salary, method = c("pearson", "kendall", "spearman"))
cor(top10, salary, method = c("pearson", "kendall", "spearman"))

cor.test(top10, salary, method=c("pearson", "kendall", "spearman"))
```

```{r}
###Scatter plots for correlated variables
plot(top10, salary)
plot(gradrate, salary)

```

```{r}
#Normalize data

normalize <- function(x){
 (x - min(x)) / (max(x) - min(x))
}
```


